Fair Decision Making

### 2023-06-22 Notes/paper_notes.tex
Added some paper notes.

>>>>

\subsection{\href{https://hci.stanford.edu/courses/cs335/2020/sp/dimsonthomas_86285_6198916_report.pdf}{Translating from Unfair to Fair Embeddings}}

\begin{approach*}
Use a translator network (a neural network) to produce an alternative embedding for a given photo. The translator network assumes nothing about the structure or training procedure for the original embeddings. \\

The overall goal is to preserve as much of the original embedding as possible while removing any encoding of protected attributes.
\end{approach*}

\begin{discussion*}
In our own experiments, we can think about their loss function choice (backed up by other work in literature) and their overall procedure.
\end{discussion*}
